Box 1 - TDT Curves

### 2023-09-20 ms/ms.qmd
clean table

```{r, tbl-1}
#| label: tbl-1
#| tbl-cap: Estimated parameters for each of the 8 new species. 
flextable(txt) %>% align(align = "center", part = "all") %>% font(fontname="Times", part = "body") %>% 
    font(fontname="Times", part = "header")  %>%  autofit()
```

>>>>

```{r, tbl-1}
#| label: tbl-1
#| tbl-cap: Estimated parameters for each of the 8 new species. 
labels <- c("Species", "Slope", "CTMax")

flextable(txt) %>% 
    align(align = "center", part = "all") %>% 
    font(fontname="Times", part = "body") %>% 
    font(fontname="Times", part = "header")  %>%  
    flextable::compose(i = 1, j = 1:3, part = "header", value= as_paragraph(as_b(labels))) %>% 
    autofit()  
```
